`phyr`: An R package for model-based phylogenetic analyses

### 2018-11-02 ms.Rmd
update pd

---
title: "`phyr`: An R package for model-based phylogenetic analyses"
author: "Daijiang Li, Russell Dinnage, Lucas Nell, Anthony Ives"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::word_document2: 
    toc: no
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
fontsize: 12pt
link-citations: yes
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/methods-in-ecology-and-evolution.csl
bibliography: ref.bib
---

```{r knitr_options, include = FALSE}
if(!require("xfun")) devtools::install_github("yihui/xfun")
if(!require("phyr")) devtools::install_github("daijiang/phyr")
xfun::pkg_attach2(c("knitr", "kableExtra", "dplyr"))
# opts_knit$set(root.dir = normalizePath("../"))
opts_chunk$set(fig.align='center', cache = FALSE, warning = FALSE, 
               message = FALSE, echo = TRUE)
options(digits = 3, width = 88)
```

@@

Example of citations: [@r2017], [@ives2011generalized]

Testing citation of Tony's new book [Dinnage]: [@ives2018book] (BTW, n.p. means No Place, and Author is in place of publisher, since the book is self-published)

@@

A table with all main functions

@@

## Cor_phy

## Phylogenetic Generalized Linear Mixed Models

@@

### Other functions

Such as `communityPGLMM.plot.re()`.

>>>>

---
title: "`phyr`: An R package for model-based phylogenetic analyses"
author: "Daijiang Li, Russell Dinnage, Lucas Nell, Anthony Ives"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    number_sections: no
    theme: sandstone
    toc: yes
    css: style.css
  bookdown::word_document2: 
    toc: no
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
fontsize: 12pt
link-citations: yes
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/methods-in-ecology-and-evolution.csl
bibliography: ref.bib
---

```{r knitr_options, include = FALSE}
if(!require("xfun")) devtools::install_github("yihui/xfun")
if(!require("phyr")) devtools::install_github("daijiang/phyr")
xfun::pkg_attach2(c("phyr", "knitr", "kableExtra", "kableExtra", "tidyverse"))
# opts_knit$set(root.dir = normalizePath("../"))
opts_chunk$set(fig.align='center', cache = FALSE, warning = FALSE, 
               message = FALSE, echo = TRUE)
options(digits = 3, width = 88, knitr.kable.NA = '')

comm = phyr::comm_a
set.seed(1234)
comm = comm[sample(nrow(comm), 5), sample(ncol(comm), 5)]
comm$site = row.names(comm)
dat = tidyr::gather(comm, key = "sp", value = "freq", -site) %>% 
  left_join(phyr::envi, by = "site") %>% 
  left_join(phyr::traits, by = "sp")
dat$pa = as.numeric(dat$freq > 0)
dat$freq2 = 20 - dat$freq
pglmm_example = phyr::communityPGLMM(freq ~ 1 + shade + (1 | sp__) + (1 | site) + (1 | sp__@site), 
                     data = dat, tree = phyr::phylotree)
```

@@

Example of citations: [@r2017], [@ives2011generalized; @ives2018book]

@@

Main functions in `phyr` can be categorized into three groups (Table \@ref(tab:mainFunc)): A) phylogenetic diversity (alpha and beta), B) species' characteristics (e.g. correlations among traits, relationships between traits and environmental variables), and C) community assembly.

(ref:maunFuncCaption) Main functions in `phyr`.

```{r mainFunc, echo=FALSE}
read.csv("phyr_func.csv", check.names = FALSE) %>% 
  knitr::kable(caption = "(ref:maunFuncCaption)", booktab = T) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "scale_down", "hover"),
                latex_options = c("striped")) %>% 
  kableExtra::column_spec(2, width = "25%")
```

@@

The set of functions to calculate phylogenetic alpha (`psv`, `pse`, `psr`, `psc`, and `psd`) and beta (`pcd`) diversity was imported from the R package `picante` [@kembel2010picante]. Their theoretic bases were provided by @helmus2007phylogenetic (for alpha diversity) and @ives2010phylogenetic (for pairwise beta diversity). We improved the speed of these functions by rewriting key parts of the codes with c++. We added one argument `prune.tree` to the set of phylogenetic alpha diversity functions to allow users to decide whether to prune the phylogeny before converting it into a variance-covariance matrix; its default value is `FALSE`, which means that the phylogeny will first been converted into a variance-covariance matrix; the matrix was then subsetted to the keep only the species interested. These two methods of generating the variance-covariance matrix may have different results in some situations. We set the default to `FALSE` because this may give a more accurate matrix.

## Species' characteristics

`cor_phy`

`binaryPGLMM`

## Community assembly

`communityPGLMM` or `pglmm`

@@

### Other help functions

Such as `communityPGLMM.plot.re()`. We can use it to show the design matrices' structures of random terms in `communityPGLMM()`. An example can be shown in Figure \@ref(fig:reStructure).

(ref:reStructureCaption) A figure to show the structures of design matrices of random terms in `communityPGLMM`.

```{r reStructure, fig.width=6, fig.height=6, fig.cap="(ref:reStructureCaption)"}
communityPGLMM.plot.re(x = pglmm_example, show.image = TRUE, show.sim.image = FALSE)
```
